Check links on old pages

### 2024-06-25 src/audit-old-pages.Rmd
Started work on audit-old-pages

path1 <- "c:/Users"
path2 <- "dropbox/professional/fun stuff/update-website"

list.files(path1) %>%
  str_subset("(Simons)|(steve)") -> me

path3 <- glue("{path1}/{me}/{path2}")

print(glue("Searching in {path3}"))

list.files(path3)
```

```{r search-files}
key_text <- "<p>This page"
n_files <- 0
n_unlinked <- 0
for (sub_dir in sub_dir_list) {
  # List all html files in a specific folder
  full_path <- glue("{path3}/{sub_dir}/") 
  full_path %>%
    list.files %>%
    str_subset("html$") -> html_list
  i_files <- length(html_list)
  i_unlinked <- 0
  for (fn in html_list) {
    # Read text from html files
    file_text <- read_lines(glue("{full_path}/{fn}"))
    # Search for key phrase
    key_line <- str_subset(file_text, key_text)
    if (length(key_line) > 0) {next}
    # List files without key phrase
    i_unlinked <- i_unlinked + 1
    print(glue("{sub_dir}/{fn} has no link to new page"))
  }
  cat("\n")
  print(glue("{sub_dir} has {i_files} files. {i_unlinked} are unlinked."))
  cat("\n")
  n_files <- n_files + i_files
  n_unlinked <- n_unlinked + i_unlinked
}
print(glue("All directories have a total of  {n_files} files. {n_unlinked} are unlinked."))
```

>>>>

path_prefix <- "c:/Users"
path_suffix <- "dropbox/professional/fun stuff/update-website"

list.files(path_prefix) %>%
  str_subset("(Simons)|(steve)") -> me

full_path <- glue("{path_prefix}/{me}/{path_suffix}")

print(glue("Searching in {full_path}"))

list.files(full_path)
```

```{r search-files}
key_text <- "<p>This page"
n_files <- 0
n_unlinked <- 0
for (sub_dir in sub_dir_list) {
  # List all html files in a specific folder
  subd_path <- glue("{full_path}/{sub_dir}/") 
  subd_path %>% 
    list.files %>%
    str_subset("html$") -> html_list
  i_files <- length(html_list)
  i_unlinked <- 0
  for (fn in html_list) {
    # Read text from html files
    file_text <- read_lines(glue("{subd_path}/{fn}"))
    # Search for key phrase
    key_line <- str_subset(file_text, key_text)
    if (length(key_line) > 0) {next}
    # List files without key phrase
    i_unlinked <- i_unlinked + 1
    print(glue("{sub_dir}/{fn} has no link to new page"))
  }
  cat("\n")
  print(glue("{sub_dir} has {i_files} files. {i_unlinked} are unlinked."))
  cat("\n")
  n_files <- n_files + i_files
  n_unlinked <- n_unlinked + i_unlinked
}
print(glue("All directories have a total of  {n_files} files. {n_unlinked} are unlinked."))
```
